From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-05 Pi+/paper/finite.tex
Update section titles
Revising sec 4

\section{The groupoid of finite types}~\label{sec:finite}

In the previous~\cref{sec:ufin}, we established that paths in $\UFin$ are equivalent to families of loops on $\Fin{n}$
for every $n:\Nat$, that is, automorphisms of finite sets of size $n$. The loopspace has a group structure -- the
identity function is the neutral element, group multiplication is given by function composition, and the group inverse
is given by inverting the bijection. This is also known to be the finite symmetric group $\Sn[n]$. In the following
sections, we will characterise these permutations syntactically.

In order to study syntactic descriptions of permutations, we need to decide whether two descriptions refer to the same
permutation. This problem is well known in group theory as the \emph{word problem} for $\Sn$. Putting it in this form
also allows us to connect to the broader scope of computational group theory and combinatorics -- we borrow ideas such
as Coxeter relations and Lehmer codes from there.

The goal of this section is to reconcile two different approaches to defining the symmetric group -- as an automorphism
group, and as a group presented using generators and relations.

\subsection{Groups}

@@

\begin{toappendix}
  \begin{definition}~\label{def:group}
    In type theory, a group $G$ can be defined as a set $S$ with the following pieces of data:

@@

However, more conveniently, in HoTT, we can instead use groupoids to talk about groups internally. A group can be
identified with a 1-object groupoid, using a technique called delooping. The delooping of a group $G$ is a groupoid
$\B{G}$, with a unique object $\pt$, where the group elements are encoded as self-loops $\pt \id_{\B{G}} \pt$.

The group operations are automatically given by operations on the identity type, with $\refl_{\pt}$ for the neutral
element, path composition for the group multiplication, and path inverse for the group inverse. These satisfy the group
laws, up to the identity type, using the groupoid coherence laws.

Since groups are sets, these 2-paths are propositions, making $\B{G}$ a 1-groupoid. Hence, a group is simply given by a
pointed, connected 1-type~\cite*{buchholtzHigherGroupsHomotopy2018,symmetryBook2021}. \footnote{This technique also
  allows defining higher groups in HoTT, as done in~\cite{buchholtzHigherGroupsHomotopy2018}.}

% For example, given a pointed type $(A:\UU, a:A)$, the automorphism group structure at $a$ is given by $a \id_{A} a$. Of
% course, for 1-groups we will require that $a \id_{A} a$ is a set, which is enforced by having $A$ be a groupoid. In our
% running example for the permutation group on finite sets, we have that $\Fin[n]$ is a set, and hence, $\UFin[n] \defeq
% \BAut[\Fin[n]]$ is a pointed, connected 1-type. Its loopspace $\loopspace[\BAut[\Fin[n]],F_{n}]$ is equivalent to
% $\Aut[\Fin[n]] \defeq (\Fin[n] \eqv \Fin[n]) \eqv (\Fin[n] \id_{\UU} \Fin[n])$, which has the corresponding automorphism
% group structure.

@@

Usually, there are are many equations, besides the group axioms, that hold for the elements of a group. For example, in
the group $\Aut[\Bool]$, or $\mathbb{Z}_2$, we have an equation $1 + 1 = 0$, which is not a consequence of the group
axioms, but is specific to this particular group. A free group has the property that no other equations hold except the
ones directly implied by the group axioms. To be able to give an equational presentation of a group, we start by
constructing the free group, then show how to add new equations to it.

Given any set $A$, we can describe the free group $F(A)$ -- we call $A$ the generating set of $F(A)$. We draw the
elements from $A$, close them under the group operations, and identify them by the group axioms. For example, the
additive group of integers $\mathbb{Z}$ is the free group on the singleton. In HoTT, we can use a higher inductive type
to define the free group, by adding path constructors for the axioms we want (see~\cref{def:free-group}).

@@

A group homomorphism between groups $G$ and $H$, which we write as $G \to^G H$, is a function between the underlying
sets that preserves the group structure. The universal property of free groups, stemming from the free-forgetful
adjunction between the category of groups and sets, follows from the induction principle for $F(A)$. Informally, it
states that if we know how a map $f$ acts on the generating set $A$, we know exactly how it acts on every element of the
group $F(A)$.

\begin{proposition}[Universal Property of $F(A)$]~\label{prop:free-groups}
  Given a group $G$ and a map $f : A \to G$, there is a unique group
  homomorphism $\extend{f} : F(A) \to^G G$ such that $\extend{f} \comp \eta_A
    \htpy f$. Equivalently, composition with $\eta_A$ gives an equivalence $F(A)
    \to^G G \eqv A \to G$. Alternatively, the type of group homomorphisms $h :
    F(A) \to^G G$ satisfying $h \comp \eta_A \htpy f$ is contractible.

@@

Although the description of $F(A)$ discussed above is close to the intuitive universal-algebraic definition, it is not
the most convenient one to work with. Besides the elements of the group, we also want to characterise its the path
space. This definition of $F(A)$ has lots of path constructors corresponding to each group axiom, making it difficult to
describe its path space.

@@

A presentation of a group builds it by starting from the free group $F(A)$ and introducing a collection of equations
that have to be satisfied in the resulting group. For example, if we take $F(\unit) \defeq \mathbb{Z}$ and add an
equation $1 + 1 = 0$, the resulting group would be $\mathbb{Z}_2 \eqv \Aut[\Bool]$. Note that not all groups have finite
(or computable) presentations, and, a group can have any number of different presentations.

\begin{definition}
  Let $A$ be a set and $R : \List[A + A] \to \List[A + A] \to \UU$ a binary relation on $\List[A + A]$. The group
  $F(\langle A ; R \rangle)$ presented by $A$ and $R$, is given by the set-quotient of the free group $F(A)$ by the
  closure of $R$.
\end{definition}

The universal property of the above definition allows for properly extending the relation on the generating set to the
whole group.\vc{check!}

\begin{proposition}[Universal property of $F(\langle A ; R \rangle)$]
  Given a group $G$ and a map $f : A \to G$ that respects $R$, there is a unique group homomorphism 
  $\extend{f} : F(\langle A ; R \rangle) \to^G G$ such that $\extend{f} \comp \eta_A \htpy f$.
\end{proposition}

To relate this to our original problem, the generators of the group can be thought of as the primitive combinators in a
(reversible) programming language, the group structure gives the composition and inversion operations, and the relations
describe how these primitive operations interact with each other.

As we mentioned, instead of operating directly with a particular group, we focus on the syntactic presentation. While
before, the only way to decide the equality of two elements in the group was to compute and check them on the nose, now
it is reduced to a \emph{word problem}, that is, deciding whether one word -- a representative of the group elements'
equivalence class, can be reduced to another word, using the group's relations. This can be thought of as a rewriting
system. However, these equations are not directed, so it is not always possible to construct a well-behaved rewriting
system. In general, the word problem for groups is proven to be undecidable.

\jk{Example?}
\todo{Examples: empty relation, full relation, van Kampen of $\pi_{1}$}

We have already seen that the group of permutations, or the symmetric group $\Sn$, can be defined by taking the type
$\Aut[\Fin[n]]$ as the underlying set, and showing that it has the appropriate group structure. Now we're going to give
a presentation for it, by defining a set of generators and relations.

There is an element of choice here -- as we already mentioned, a group can be presented in many different ways. For
example, we could generate the permutation group on $\Fin[n]$ by using generators that:

\begin{itemize}
  \item swap the $i$-the element with the $(i+1)$-th element, that is, adjacent swaps, or
  \item swap the $i$-th element with the $j$-th element, for arbitrary $i$-s and $j$-s, or
  \item swap the $i$-th element with an element at a fixed position, or
  \item flip a prefix $\Fin[k]$ of $\Fin[n]$ for $k \leq n$, or
  \item cyclically shift any subset of $\Fin[n]$.
\end{itemize}

One way of thinking about these presentations is via sorting algorithms, which use different primitive operations. A
sorting algorithm has to calculate a permutation of a list or a finite set, which satisfies the invariant of being a
sorted sequence, which means, the primitive operations of a sorting algorithm are able to generate all the permutations
on a given list. So, a chosen set of reversible operations in a sorting algorithm can be a good candidate for the
generators of a permutation group.

For example, bubble sort uses the primitive operation of adjacent swaps, insertion sort and selection sort use the
primitive operation of swapping the $i$-th element with the $j$-th element, cycle sort uses cyclical shifts of
subsequences, pancake sort uses flips of prefixes of the list, et cetera~\todo{check!}. The choice of generators for our
presentation is important for the following reasons.

We use a presentation based on adjacent transpositions for generators, called a~\emph{Coxeter presentation}, which we
also use to solve the word problem for $\Sn$. Connecting it back to the language $\PiLang$, we will show that it is
possible to encode all $\PiLang$ combinators using adjacent transpositions (in~\cref{sec:equivalence}).

@@

The primitive operations we use are going to be adjacent swaps. When dealing with permutations on an $n + 1$-element
set, there are $n$ adjacent transpositions, transposition number $k$ swapping elements $\el{k}$ and $\el{k+1}$. Thus,
the generating set would be $\Fin[n]$. There are three relations that we're going to specify for this presentation --
these are the laws that these generators should satisfy. It is easiest to visualise them as braid diagrams.

First, swapping the same two elements two times in a row should be the same as doing nothing:

\[
  \begin{tabular}{m{0.3\linewidth}m{0.1\linewidth}m{0.3\linewidth}}
    \begin{center}
      \begin{tikzpicture}
        \pic[local bounding box=my braid,braid/.cd,
          number of strands = 2,
          thick]
        {braid={ s_1, s_1}};
      \end{tikzpicture}
    \end{center}
     &
    \(\xlongrightarrow[]{\cancel}\)
     &
    \begin{center}
      \begin{tikzpicture}
        \pic[local bounding box=my braid,braid/.cd,
          number of strands = 2,
          thick]
        {braid={1, 1}};
      \end{tikzpicture}
    \end{center}
  \end{tabular}
\]

Second, when swapping two distinct pairs of elements (i.e. when the indices of two transpositions differ by at least 1),
it should not matter in which order the swapping happens, that is, we can slide the wires freely.

\[
  \begin{tabular}{m{0.3\linewidth}m{0.1\linewidth}m{0.3\linewidth}}
    \begin{center}
      \begin{tabular}{m{0.3\linewidth}m{0.1\linewidth}m{0.3\linewidth}}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 2,
            thick]
          {braid={ 1, s_1}};
        \end{tikzpicture}
         &
        \(\cdots\)
         &
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 2,
            thick]
          {braid={ s_1, 1 }};
        \end{tikzpicture}
      \end{tabular}
    \end{center}
     &
    \(\xlongrightarrow[]{\swap}\)
     &
    \begin{center}
      \begin{tabular}{m{0.3\linewidth}m{0.1\linewidth}m{0.3\linewidth}}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 2,
            thick]
          {braid={ s_1, 1}};
        \end{tikzpicture}
         &
        \(\cdots\)
         &
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 2,
            thick]
          {braid={ 1, s_1}};
        \end{tikzpicture}
      \end{tabular}
    \end{center}
  \end{tabular}
\]

The previous two cases were for the transpositions that either completely overlap, or not overlap at all. The third case
says what happens if we perform transpositions that move the same elements. If the next transposition in the sequence is
equal to the the first one, we endorce a third law -- the braiding relation.

\[
  \begin{tabular}{m{0.3\linewidth}m{0.1\linewidth}m{0.3\linewidth}}
    \begin{center}
      \begin{tikzpicture}
        \pic[local bounding box=my braid,braid/.cd,
          number of strands = 3,
          thick]
        {braid={ s_2, s_1, s_2}};
      \end{tikzpicture}
    \end{center}
     &
    \(\xlongrightarrow[]{\braid}\)
     &
    \begin{center}
      \begin{tikzpicture}
        \pic[local bounding box=my braid,braid/.cd,
          number of strands = 3,
          thick]
        {braid={ s_1, s_2, s_1}};
      \end{tikzpicture}
    \end{center}
  \end{tabular}
\]

\todo{an example/motivation from book.pdf}

This construction is called a Coxeter presentation. Writing it formally, we take the generating set to be $\Fin[n]$,
where the element $k$ corresponds to an adjacent transpositions $\tau_k$, which swaps elements $\el{k}$ and $\el{k+1}$.
Then, we define a binary relation $\cox$ on $\List[\Fin[n]]$, which encodes the laws discussed above.

\begin{definition}[$\cox$]
  \begin{align*}
    \cancel
     & : \forall n \to (n \cons n \cons \nil) \cox \nil                                                     \\
    \swap
     & : \forall k, n \to (\suc[k] < n) \to (n \cons k \cons \nil) \cox (k \cons n \cons \nil)              \\
    \braid
     & : \forall n \to (\suc[n] \cons n \cons \suc[n] \cons \nil) \cox (n \cons \suc[n] \cons n \cons \nil) \\
  \end{align*}
\end{definition}

We define $\cox*$ as the congruence closure of $\cox$.

\begin{definition}[$\cox*$]
  \begin{align*}
    \reflr{\cox}
     & : \forall w \to w \cox* w                                                                                                           \\
    \symr{\cox}
     & : \forall w_{1}, w_{2} \to w_{1} \cox* w_{2} \to w_{2} \cox* w_{1}                                                                  \\
    \transr{\cox}
     & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \cox* w_{2} \to w_{2} \cox* w_{3} \to w_{1} \cox* w_{3}                                    \\
    \congrf{\cox}{\append}
     & : \forall w_{1}, w_{2}, w_{3}, w_{4} \to  w_{1} \cox* w_{2} \to w_{3} \cox* w_{4} \to w_{1} \append w_{3} \cox* w_{2} \append w_{4} \\
    \relr{\cox}
     & : \forall w_{1}, w_{2} \to w_{1} \cox w_{2} \to w_{1} \cox* w_{2}                                                                   \\
  \end{align*}
\end{definition}

To solve the word problem for $\Sn$, we turn the relations into a rewriting system $(\List[\Fin[n]],\cox*)$. A normal
form of an element can then be computed by following the rewrite rules, and two words can be compared for
$\cox*$-equality by comparing their normal forms. A well-behaved rewriting system has to be strongly normalising and
confluent. First, we observe that after throwing out reflexivity and symmetry, the right hand sides of the relations
$\cox*$ are strictly smaller than the left hand sides, in terms of the lexicographical ordering on words in $\Fin[n]$.
Thus, by directing the relation from left to right, we would get the termination property out of the box.

The system also has to be confluent, meaning that all critical pairs, that is, terms with overlapping possible reduction
rules, have to converge. For example, the pairs below converge.

\[
  \begin{array}{lcr}
    \gspan[\braid][\braid]{\tau_2\tau_1\tau_2\tau_1\tau_2}{\tau_1\tau_2\tau_1\tau_1\tau_2}{\tau_2\tau_1\tau_1\tau_2\tau_1}
     &
    \text{or}
     &
    \gspan[\braid][\cancel]{\tau_2\tau_1\tau_2\tau_2}{\tau_1\tau_2\tau_1\tau_2}{\tau_2\tau_1}
  \end{array}
\]

>>>>

\section{The Group of Permutations}~\label{sec:finite}

In~\cref{sec:ufin}, we established that paths in $\UFin$ are equivalent to families of loops on $\Fin[n]$ for every
$n:\Nat$, that is, automorphisms of finite sets of size $n$, with the loopspace encoding the automorphism group.This is
also known to be the finite symmetric group $\Sn[n]$. In the following sections, we will describe this group
syntactically.

In order to study syntactic descriptions of permutations, we need to decide whether two descriptions refer to the same
permutation. This is the \emph{word problem} for $\Sn$. Putting it in this form also allows us to connect it to the
broader scope of computational group theory and combinatorics -- we borrow ideas such as Coxeter relations and Lehmer
codes from there.

The goal of this section is to reconcile two different approaches to defining the symmetric group -- as an automorphism
group, and as a group presented using generators and relations. The generators of the group can be thought of as the
primitive combinators in a (reversible) programming language, the group structure gives the composition and inverse
operations, and the relations describe how these primitive combinators interact with each other.

One way of thinking about presentations of $\Sn$ is via sorting algorithms, which use different primitive operations. A
sorting algorithm has to calculate a permutation of a list or a finite set, which satisfies the invariant of being a
sorted sequence, which means, the primitive operations of a sorting algorithm are able to generate all the permutations
on a given list. So, a chosen set of reversible operations in a sorting algorithm can be a good candidate for the
generators of a permutation group. For example, we could generate the permutation group on $\Fin[n]$ by using generators
(primitive operations) that:

\begin{itemize}
  \item swap the $i$-th element with the $(i+1)$-th element, that is, adjacent swaps, or
  \item swap the $i$-th element with the $j$-th element, for arbitrary $i$-s and $j$-s, or
  \item swap the $i$-th element with an element at a fixed position, or
  \item flip a prefix $\Fin[k]$ of $\Fin[n]$ for $k \leq n$, or
  \item cyclically shift any subset of $\Fin[n]$.
\end{itemize}

Bubble sort uses the primitive operation of adjacent swaps, insertion sort and selection sort use the primitive
operation of swapping the $i$-th element with the $j$-th element, cycle sort uses cyclical shifts of subsequences,
pancake sort uses flips of prefixes of the list, et cetera~\todo{check!}. The choice of generators for our presentation
is important for the following reasons.

We use a presentation based on adjacent transpositions for generators, called a~\emph{Coxeter presentation}, which we
also use to solve the word problem for $\Sn$. Connecting it back to the language $\PiLang$, we will show that it is
possible to encode all $\PiLang$ combinators using adjacent transpositions (in~\cref{sec:equivalence}). The rest of this
section develops these intuitions formally. Group presentations are built by adding equations to a \emph{free group},
which we define first.

\begin{toappendix}
  \subsection{Groups}

@@

  \begin{definition}~\label{def:group}
    In type theory, a group $G$ can be defined as a set $S$ with the following pieces of data:

@@

@@

Usually, there are are many equations, besides the group axioms, that hold for the elements of a group. For example, in
the group $\Aut[\Bool]$, or $\mathbb{Z}_2$, we have an equation $1 + 1 = 0$, which is not a consequence of the group
axioms, but is specific to this particular group. A free group has the property that no other equations hold except the
ones directly implied by the group axioms. For example, the additive group of integers $\mathbb{Z}$ is the free group on
the singleton set.

@@

A group homomorphism between groups $G$ and $H$, which we write as $G \to^G H$, is a function between the underlying
sets that preserves the group structure. Giving a group homomorphism out of the free group is equivalent to giving a
function out of the generating set. This is the universal property of free groups, stemming from the free-forgetful
adjunction between the category of groups and sets.

% Informally, it states that if we know how a map $f$ acts on the
% generating set $A$, we know exactly how it acts on every element of the group $F(A)$.

\begin{proposition}[Universal Property of $F(A)$]
  \label{prop:free-groups}
  Given a group $G$ and a map $f : A \to G$, there is a unique group
  homomorphism $\extend{f} : F(A) \to^G G$ such that $\extend{f} \comp \eta_A
    \htpy f$. Equivalently, composition with $\eta_A$ gives an equivalence $F(A)
    \to^G G \eqv A \to G$. Alternatively, the type of group homomorphisms $h :
    F(A) \to^G G$ satisfying $h \comp \eta_A \htpy f$ is contractible.

@@

Following the universal-algebraic definition, in HoTT, we could use a naive higher inductive type to define the free
group, which enforces the group axioms by adding path constructors (see~\cref{def:free-group} for the full definition).
Using the induction principle, we can easily verify the universal property. However, since this definition of $F(A)$ has
lots of path constructors corresponding to each group axiom, characterising its path space is difficult.

@@

A presentation of a group builds it by starting from the free group $F(A)$ and introducing additional equations that are
satisfied in the resulting group. For example, if we take $F(\unit) \defeq \mathbb{Z}$ and add an equation $1 + 1 = 0$,
the resulting group would be $\mathbb{Z}_2 \eqv \Aut[\Bool]$. Note that not all groups have finite (or computable)
presentations, and, a group can have any number of different presentations.

\begin{definition}
  Let $A$ be a set and $R : \List[A + A] \to \List[A + A] \to \UU$ a binary relation on $\List[A + A]$. The group
  $F(\langle A ; R \rangle)$ presented by $A$ and $R$, is given by the set-quotient of the free group $F(A)$ by the
  congruence closure of $R$.
\end{definition}

The universal property of the above definition is similar to~\cref{prop:free-groups} except the relation has to be
preserved by the function mapping out of the generating set.

\begin{proposition}[Universal property of $F(\langle A ; R \rangle)$]
  Given a group $G$ and a map $f : A \to G$, such that $f$ extended to $F(A)$ respects $R$, there is a unique group
  homomorphism $\extend{f} : F(\langle A ; R \rangle) \to^G G$ such that $\extend{f} \comp \eta_A \htpy f$.
\end{proposition}

Before, the only way to decide the equality of two elements in a group was to compute and check them on the nose, but in
a group presentation, this is reduced to a \emph{word problem}, that is, deciding whether one word -- a representative
of the equivalence class of the group's elements, can be reduced to another word, using the group's relations. However,
these equations are not directed, so it is not always possible to construct a well-behaved rewriting system. In general,
the word problem for groups is known to be undecidable.\jk{Example?}\todo{Examples: empty relation, full relation, van
  Kampen of $\pi_{1}$}

% This can be thought of as word reductions in a rewriting system.

@@

To present the group $\Sn$, the primitive operations we are going to use will be adjacent swaps. When dealing with
permutations on an $n + 1$-element set, there are $n$ adjacent transpositions, transposition number $k$ swapping
elements $(\el{k}, \el{k+1})$. Thus, the generating set would be $\Fin[n]$. There are three relations that we're going
to specify for this presentation -- these are the equations that these generators should satisfy. We visualise them as
braid diagrams in~\cref{fig:coxeter-braid}.

\begin{enumerate}
  \item[\labelcref{fig:coxeter-a}] Swapping the same two elements two times in a row should be the same as doing nothing
  \item[\labelcref{fig:coxeter-b}] When swapping two distinct pairs of elements, it should not matter in which order the
    swapping happens, that is, we can slide the wires freely.
  \item[\labelcref{fig:coxeter-c}] If the next transposition in the sequence is equal to the the first one, the order of
    operations can be reversed.
\end{enumerate}

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\Huge] at (2, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd, 
      number of strands = 2,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.3cm,
      thick] at (0, 0)
      {braid={ 1, s_1}};
      \node[] at (1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd, 
      number of strands = 2,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.3cm,
      thick] at (1.5, 0)
      {braid={ s_1, 1}};
      \node[font=\Huge] at (3, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd, 
      number of strands = 2,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.3cm,
      thick] at (4, 0)
      {braid={ 1, s_1}};
      \node[] at (5.2, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd, 
      number of strands = 2,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.3cm,
      thick] at (5.5, 0)
      {braid={ s_1, 1}};
  \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\Huge] at (2, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (3, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}
\todo{an example/motivation from book.pdf}

This construction is called a Coxeter presentation of $\Sn$. Writing it formally, we encode the rules discussed above
using a relation $\cox$ on $\List[\Fin[n]]$, and then take its congruence closure $\cox*$.

\begin{definition}[$\cox : {\List[\Fin[n]]} \to {\List[\Fin[n]]} \to {\UU}$]
  \begin{align*}
    \cancel
     & : \forall n \to (n \cons n \cons \nil) \cox \nil                                                     \\
    \swap
     & : \forall k, n \to (\suc[k] < n) \to (n \cons k \cons \nil) \cox (k \cons n \cons \nil)              \\
    \braid
     & : \forall n \to (\suc[n] \cons n \cons \suc[n] \cons \nil) \cox (n \cons \suc[n] \cons n \cons \nil) \\
  \end{align*}
\end{definition}
\begin{definition}[$\cox* : {\List[\Fin[n]]} \to {\List[\Fin[n]]} \to {\UU}$]
  \begin{align*}
    \reflr{\cox}
     & : \forall w \to w \cox* w                                                                                                           \\
    \symr{\cox}
     & : \forall w_{1}, w_{2} \to w_{1} \cox* w_{2} \to w_{2} \cox* w_{1}                                                                  \\
    \transr{\cox}
     & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \cox* w_{2} \to w_{2} \cox* w_{3} \to w_{1} \cox* w_{3}                                    \\
    \congrf{\cox}{\append}
     & : \forall w_{1}, w_{2}, w_{3}, w_{4} \to  w_{1} \cox* w_{2} \to w_{3} \cox* w_{4} \to w_{1} \append w_{3} \cox* w_{2} \append w_{4} \\
    \relr{\cox}
     & : \forall w_{1}, w_{2} \to w_{1} \cox w_{2} \to w_{1} \cox* w_{2}                                                                   \\
  \end{align*}
\end{definition}

The idea for solving the word problem for $\Sn$ is to turn these undirected relations into a terminating rewriting
system $(\List[\Fin[n]],\cox*)$, so that, by repeatedly applying the reduction rules as long as possible, any two
$\cox*$-equal terms would eventually converge to the same normal form.

For this to work, we first need the system to have the strong normalisation property, meaning that there are no infinite
reductions. We observe that after throwing out reflexivity and symmetry, the right hand sides of the relations $\cox*$
are strictly smaller than the left hand sides, in terms of the lexicographical ordering on words in $\Fin[n]$ (which is
well-founded). Thus, by directing the relation from left to right, we would get the termination property out of the box.
Second, we need the normal forms to be unique, so that we can get a normalisation function. This will be true if the
rewriting system is confluent -- meaning that all critical pairs, that is, terms with overlapping possible reduction
rules, have to converge. For example, in our system, the pairs in~\cref{fig:critical-pairs-converge} converge.
Unfortunately, this is not true for all critical pairs -- an  example is in~\cref{fig:critical-pairs-non-converging},
where both endpoints are normal with respect to the $\cox*$ relation.

% \begin{figure}
% \[
%   \begin{array}{lcr}
%     \gspan[\braid][\braid]{\tau_2\tau_1\tau_2\tau_1\tau_2}{\tau_1\tau_2\tau_1\tau_1\tau_2}{\tau_2\tau_1\tau_1\tau_2\tau_1}
%      &
%     \text{or}
%      &
%     \gspan[\braid][\cancel]{\tau_2\tau_1\tau_2\tau_2}{\tau_1\tau_2\tau_1\tau_2}{\tau_2\tau_1}
%   \end{array}
% \]
% \caption{Critical pairs}
% \label{fig:critical-pairs}
% \end{figure}

\begin{figure}
  \begin{subfigure}[b]{0.45\textwidth}
    % https://q.uiver.app/?q=WzAsNixbMiwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzQsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMiwzLCJcXHRhdV8xIl0sWzQsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \adjustbox{scale=\scalef,center}{
      \begin{tikzcd}
        && {\tau_2\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_1\tau_2} &&&& {\tau_2\tau_1\tau_1\tau_2\tau_1} \\
        {\tau_1\tau_2\tau_2} &&&& {\tau_2\tau_2\tau_1} \\
        && {\tau_1}
        \arrow["\braid"', squiggly, from=1-3, to=2-1]
        \arrow["\braid", squiggly, from=1-3, to=2-5]
        \arrow["\cancel"', squiggly, from=2-1, to=3-1]
        \arrow["\cancel"', squiggly, from=3-1, to=4-3]
        \arrow["\cancel", squiggly, from=2-5, to=3-5]
        \arrow["\cancel", squiggly, from=3-5, to=4-3]
      \end{tikzcd}
    }
  \end{subfigure}
  \begin{subfigure}[]{0.45\textwidth}
    % https://q.uiver.app/?q=WzAsNSxbMiwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8yIl0sWzAsMSwiXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFsyLDQsIlxcdGF1XzJcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFsxLDMsIlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzMsNCwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDIsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV1d
    \adjustbox{scale=\scalef,center}{
      \begin{tikzcd}
        && {\tau_2\tau_1\tau_2\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_2} \\
        & {\tau_1\tau_1\tau_2\tau_1} \\
        && {\tau_2\tau_1}
        \arrow["\braid"', squiggly, from=1-3, to=2-1]
        \arrow["\cancel", squiggly, from=1-3, to=5-3]
        \arrow["\braid"', squiggly, from=2-1, to=3-1]
        \arrow["\braid"', squiggly, from=3-1, to=4-2]
        \arrow["\cancel"', squiggly, from=4-2, to=5-3]
      \end{tikzcd}
    }
  \end{subfigure}
  \caption{Converging critical pairs}
  \label{fig:critical-pairs-converge}
\end{figure}

\begin{figure}
  $\gspan[\braid][\swap]{\tau_3\tau_2\tau_3\tau_1}{\tau_2\tau_3\tau_2\tau_1}{\tau_3\tau_2\tau_1\tau_3}$
  \caption{Non-converging critical pairs}
  \label{fig:critical-pairs-non-converging}
\end{figure}
